Financial_Analysis

### 2016-07-08 financial.rmd
plotted each fold

>>>>

wot <- each.fold(methods = c("log", "rf", "boost"), df.assem = all10mice, x.folds.assem = 5,
                 iterations = 100, seed = 200)

saveRDS(wot, "C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/indiv_folds.rds")

if(.Platform$OS.type == 'windows'){
        ind_folds <- readRDS("C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/indiv_folds.rds")
} else{
        ind_folds <- readRDS("/Users/yam/Documents/github/consult/finalwriteup/report_data/indiv_folds.rds")
}

#plot profit curves for each fold
names(ind_folds) <- c(1:100)
folds_plot <- bind_rows(ind_folds, .id = "id")
folds_plot <- gather(folds_plot, key = iteration, value = profit, -threshold, - id)

temp = gsub("([:0-9:])", "\\1~", folds_plot$iteration, ignore.case = TRUE) %>% strsplit(., "~")

folds_plot$iteration = sapply(temp, function(x) x[1])
folds_plot$method = sapply(temp, function(x) x[2])

ggplot(folds_plot, aes(x = threshold, y = profit, colour = id)) +
        facet_wrap(~method) +
        geom_point()+
        # geom_line(aes(group = id)) +
        theme(legend.position = "none")
